
# Statistical Inference - Course Project



The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Set lambda = 0.2 for all of the simulations. In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.

# Results

```{r}
lambda = 0.2
n = 40
simnum = 1:1000
set.seed(123)
means <- data.frame(x = sapply(simnum, function(x) {mean(rexp(n, lambda))}))
```

#### 1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.

```{r}
### Mean of the simulated data
mean(means$x)
```

```{r}
### Expected mean
(1/lambda)
```

Therefore, the center of distribution of averages of 40 exponentials is close to the theoretical center of the distribution.

#### 2. Show how variable it is and compare it to the theoretical variance of the distribution.

```{r}
### Standard deviation of the simulated data
sd(means$x)
```

```{r}
### Expected standard deviation
(1/lambda)/sqrt(40)
```


```{r}
### Variance of the simulationed data:
var(means$x)
```

```{r}
### Variance expected
((1/lambda)/sqrt(40))^2
```
Therefore, the variability in distribution of averages of 40 exponentials is close to the theoretical variance of the distribution.

#### 3. Show that the distribution is approximately normal.
```{r global_options,echo=F,}

par(mfcol=c(1,2))
library(ggplot2)
ggplot(data = means, aes(x = x)) + 
    geom_histogram(aes(y=..density..), fill = I('blue'), 
                  binwidth = 0.20, color = I('black')) +
    stat_function(fun = dnorm, arg = list(mean = 5, sd = sd(means$x)))

 #use qqplot and qqline to compare the distribution of averages of 40 exponentials
# to a normal distribution
#qqnorm(means$x)
#qqline(means$x, col = 2)
    	      
```

From the above plot, the distribution of averages of 40 exponentials is very close to a normal distribution.

#### 4. Evaluation of the coverage of the confidence interval for 1/lambda: $\bar{X} \pm  1.96 \frac{s}{\sqrt{Sn}}$

```{r}
mean(means$x) + c(-1,1)*1.96*sd(means$x)/sqrt(nrow(means))
```